\begin{longtable}[h!]{lll}
\toprule
               &         &                                                                                          Definitions \\
Type & Variables &                                                                                                      \\
\midrule
\endfirsthead

\toprule
               &         &                                                                                          Definitions \\
Type & Variables &                                                                                                      \\
\midrule
\endhead
\midrule
\multicolumn{3}{r}{{Continued on next page}} \\
\midrule
\endfoot

\bottomrule
\endlastfoot
\multirow{9}{*}{Time Variant} & ContainsAds &              \makecell[l]{Dummy variable equals 1 if an app \\ contains advertisement, 0 otherwise.} \\
               & OffersIAP &              \makecell[l]{Dummy variable equals 1 if an app \\ offers in-app-purchase, 0 otherwise.} \\
               & Paid &    \makecell[l]{Dummy variable equals 1 if an app charges a positive \\ price upfront, 0 otherwise.} \\
               & Price &                                                                      \makecell[l]{App price in USD.} \\
               & Post &  \makecell[l]{Dummy variable equals 1 if the observation \\ is after Mar 2020 (inclusive), and 0 if the \\ observation is before Mar 2020} \\
               & Score &                                               \makecell[l]{Demeaned rating of an app (from 1 to 5).} \\
               & Tier1 &  \makecell[l]{Dummy variable equals 1 if an  \\ app has minimum installs above 10,000,000 (inclusive),  \\ 0 otherwise.} \\
               & Tier2 &  \makecell[l]{Dummy variable equals 1 if an \\ app has minimum installs below 10,000,000 and \\ above 100,000 (inclusive), 0 otherwise.} \\
               & Reviews &                     \makecell[l]{Demeaned and standardized \\ (zscore) number of reviews of an app.} \\
\cline{1-3}
\multirow{4}{*}{Time Invariant} & ContentRatingAdult &                  \makecell[l]{Dummy variable equals 1 if the app has \\ adult content, 0 otherwise.} \\
               & Size &                                                                              \makecell[l]{Size (MB)} \\
               & DaysReleased &                     \makecell[l]{Number of days since the app was \\ launched on Google Play Store.} \\
               & TopFirm &                  \makecell[l]{Dummy variable equals 1 if the app is \\ owned by a Top Digital Firm.} \\
\end{longtable}
