---
title: "R Notebook"
author: naixin
date: 12/21/20
output: html_notebook
---
# fuzzy c clustering using ppclust
https://cran.r-project.org/web/packages/ppclust/vignettes/fcm.html

```{r}
library(ppclust)
library(dplyr)
library(factoextra)
library(cluster)
library(fclust)
library(RcppCNPy)
```

```{r}
options(digits=5)
```


```{r}
initial_panel = '201908'
folder_name = paste(initial_panel, '_PANEL_DF', sep = '')
# linux file path
INPUT_path = file.path("/home/naixin/Insync/naixin88@sina.cn/OneDrive/_____GWU_ECON_PHD_____/___Dissertation___/____WEB_SCRAPER____/__PANELS__", folder_name)
filename = file.path(INPUT_path, 'svd_matrix_transformed.npy')
svd_matrix = npyLoad(filename)
```

FCM is usually started by using an integer specifying the number of clusters. In this case, the prototypes matrix is internally generated by using any of the prototype initalization algorithms which are included in the package ‘inaparc’. The default initialization technique is K-means++ with the current version of fcm function in this package. In the following code block, FCM runs for three clusters with the default values of the remaining arguments.

```{r}
res.fcm <- fcm(svd_matrix, centers=2)
```

```{r}
as.data.frame(res.fcm$u)
```

```{r}
summary(res.fcm)
```


